The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
typo

For eight stars, we find that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu. One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model. The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ and used it to calibrate the convective overshoot parameter for low-luminosity red giants. The bulk asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.

>>>>

For eight stars, we find that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu. One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model. The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ and used it to calibrate the convective overshoot parameter for low-luminosity red giants. The bulk asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.
